Gamification Effectiveness on Education

### 2024-04-18 paper/paper.qmd
use lintr and styler

finalExam_model <-
  readRDS(file = here::here("models/final_exam.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Final Exam Marks" = finalExam_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

plot(finalExam_model, "trace")

plot(finalExam_model, "rhat")
```

>>>>

final_exam_model <-
  readRDS(file = here::here("models/final_exam.rds"))
```

@@

modelsummary::modelsummary(
  list(
    "Final Exam Marks" = final_exam_model
  ),
  statistic = "mad",
  fmt = 2
)
```

@@

plot(final_exam_model, "trace")

plot(final_exam_model, "rhat")
```
